Turtlebot SLAM

### 2013-01-22 trunk/Article/Article.tex
Included the abstract

\begin{abstract}
This article accompanies the research project "TurtleBot SLAM" from the Master "Artificial Intelligence" of Maastricht University.
\end{abstract}

@@

\subsection{Mapping}\label{sec:mapping}

The map is internally represented as an occupancy grid. It consists of cells which hold information about obstacles, free/- and unknown space.

>>>>

\begin{abstract}
Robots are used for a lot of tasks nowadays, to perform an assignment a robot needs a map of the environment. Using external referencing methods, like GPS, they can locate them self. Sometimes the maps are provided, making the task easier to perform. It becomes far more difficult when the robot has no map or external reference available. The task of mapping an environment can be split into two main components, namely exploration and SLAM which stands for Simultaneous Localization And Mapping. The exploration determines the path the robot takes to explore the unknown space of the environment. Exploration is based on the idea of frontiers, these are cells which separate unexplored cells from free explored cells. The exploration strategy then determines the next location the robot should move to. The SLAM part incorporates the new data as is becomes available when the robot moves to unexplored areas and takes measurements of previously unrecorded space. One intuitive way is to represent all the data as a graph where the nodes represent a pose of the robot and the edges connecting two nodes the measured constraints. The algorithm then tries to find a configuration of nodes which is maximally consistent with the constraints. This article will describe an implementation of this so called GraphSLAM with frontier exploration. All the implemented code is first tested and validated in a simulator and later run on a real robot, a TurtleBot.

This article accompanies the research project "TurtleBot SLAM" from the Master "Artificial Intelligence" of Maastricht University.
\end{abstract}

@@

\subsection{Mapping}
\label{sec:mapping}
The map is internally represented as an occupancy grid. It consists of cells which hold information about obstacles, free/- and unknown space.
